Data Management for LSST Special Programs

### 2023-10-19 DMTN-065.tex
rm team

\author{M.~L.~Graham, M.~Juri\'{c}, K.-T.~Lim, E.~Bellm, G.~Dubois-Felsmann, L.~P.~Guy, and the Data Management System Science Team}

>>>>

\author{M.~L.~Graham, Y.~AlSayyad, K.~Bechtol, E.~C.~Bellm, J.~F.~Bosch, J.~L.~Carlin, 
G.~P.~Dubois-Felsmann, L.~P.~Guy, M.~Juri\'{c}, K.-T.~Lim, E.~S.~Rykoff, C.~T.~Slater}
